Alexis Roche

### 2021-08-13 cv/cv.tex
Modif Nenuphars

\noindent Hands-on scientific team leader, graduated from \'Ecole Centrale Paris, PhD, with a specialist expertise in computer vision, data science and machine learning. Has operated in the fields of academic research, healthcare, electro-domestic and entertainment industry. Strong experience in the development of both open source and commercial software. {\em Keywords:} artificial intelligence, image processing, computer vision, medical image analysis, machine learning, deep learning, statistics, Python,~C.

>>>>

\noindent Hands-on scientific team leader, graduated from \'Ecole Centrale Paris, PhD in engineering science, with a specialist expertise in computer vision, data science and machine learning. Has operated in the fields of academic research, healthcare, electro-domestic and entertainment industry. Strong experience in the development of both open source and commercial software. {\em Keywords:} applied mathematics, artificial intelligence, image processing, computer vision, medical image analysis, machine learning, deep learning, statistics, Python,~C.
